% Chris Gibson's Resume
% URL: 
%
% Based on resume tex file by Kamil Wojcicki
% URL: http://linux.dsplabs.com.au/resume-writing-example-latex-template-linux-curriculum-vitae-professional-cv-layout-format-text-p54/

\documentclass[margin,line]{resume}

\begin{document}
\name{\huge Christopher Gibson}
\begin{resume}

{
	\sc
	\color{ColorOne}
    \hfill (925)330-3571                  \vspace{0mm}\\\vspace{0mm}%
    \hfill cgibson@calpoly.edu            \vspace{0mm}\\\vspace{0mm}%
    \hfill http://www.chrisgibson.us      \vspace{0mm}\\\vspace{-4.5mm}%
}


    %__________________________________________________________________________________________________________________
    % Interests
    \section{\mysidestyle Project\\Interests}

	Computer graphics, graphics application development, visualization of data, real-time and \\
	rendered graphics.


    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{California Polytechnic University}, San Luis Obispo, California \vspace{2mm}\\\vspace{1mm}%
    \textsl{B.S/M.S of Computer Science} \hfill \textbf{ September 2006 -- present}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
    	\item Accepted into blended "4+1" B.S + M.S Program in 2009
        \item Masters concentration in computer graphics
        \item Expected graduation date: June 2011
        \item Advisors:  Dr. Zo\"{e} J. Wood
    \end{list2}\vspace{-1.5mm}


    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}

    % DreamWorks
    \textbf{DreamWorks Animation}, Redwood City, CA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Research \& Development, Lighting Team Intern} \hfill \textbf{June 2010 -- August 2010}\\
    Developed features for production-level tools in C++ and OpenGL.
    Created unit-tests, ran manual smoke tests and wrote extensive test reports on results and compiler performance.
    Worked in a large code base and handled multiple development workspaces simultaneously.

    % Yahoo Inc.
    \textbf{Yahoo! Corporation}, Sunnyvale, CA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Intern \& Contracted Developer} \hfill \textbf{June 2009 -- Winter 2009}\\
    Designed, developed and released PHP-based REST APIs and RSS feed systems for internal operations.
    Continued work as contractor through WorkForceLogic, furthering REST API development.

    % Sun Microsystems
    \textbf{Sun Microsystems}, Santa Clara, CA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Developer} \hfill \textbf{June 2008 -- September 2008}\\
    Designed and implemented an escalation management web application using java web service libraries and frameworks.
    Administrated and managed server hardware both physically and remotely.

    % CreateSpace
    \textbf{CreateSpace}, San Luis Obispo, CA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Developer} \hfill \textbf{November 2006 -- January 2008}\\
    Worked in a number of areas within the server-side code base.
    Implemented code that used SOAP messaging libraries to contact Amazon product databases for in-house applications.
    

    %__________________________________________________________________________________________________________________
    % Academia
    \section{\mysidestyle Related Academia} 

	\vspace{1mm} % Used to offset a strange alignment error between title and contents
	\begin{tabular}{@{}p{6cm}p{6cm}}
	-Distributed Systems     &  -Graduate Computer Graphics   \\
	-Parallel Computing      &  -Advanced Rendering Techniques    \\
	-Real-Time Graphics      &  -Graphics Animations                   \\
	\end{tabular}

	\textbf{Cal Poly Game Development Club}\\\vspace{1mm}%
	\textsl{President}\hfill \textbf{ November 2009 -- present}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
    	\item Organized annual 48 hour "Global Game Jam" event at cal poly for the last two years
        \item Spoke on various topics on game design \& development
    \end{list2}\vspace{-1.5mm}

	\textbf{Cal Poly ACM}\\\vspace{1mm}%
	\textsl{Corporate Liaison} \hfill \textbf{ September 2010 -- present}\vspace{-3mm}\\\vspace{-1mm}%


    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Skills}

    C, C++, Lua, PHP, Java, Python, Linux shell scripting, \LaTeX.



%______________________________________________________________________________________________________________________
\section{\mysidestyle References}

\vspace{1mm} % Used to offset a strange alignment error between title and contents
\begin{tabular}{@{}p{6cm}p{6cm}}
\textbf{Dr. Zo\"{e} J. Wood}            &  \textbf{Ignatios E. Vakalis}             \\
Professor                               &  Computer Science Department Chair        \\
California Polytechnic University,      &  California Polytechnic University,       \\
San Luis Obispo, CA                     &  San Luis Obispo, CA                      \\
phone: \textsl{available on request}    &  phone: \textsl{available on request}     \\
e-mail: \textsl{available on request}   &  e-mail: \textsl{available on request}    \\
\end{tabular}

\end{resume}
\end{document}
